Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Lemmas.tex
accepted Peter's changes
changed gaussian noise to more general sub-gaussian noise

\begin{rlemma}{Lemma}{\ref{lem:round-prob}}
Recall that $\sigma$ is the standard deviation of the Gaussian noise.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau_s$ is such that almost surely,
each arm --- and in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau_s$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau_s$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
renormalized to have standard deviation $1/2$.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{x_J^2}{16 \sigma^2}$,
and obtain that

@@

By Assmption~\ref{A1},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
is at most
$\TieDensity \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})
\leq \frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) \pfedit{\le} \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

>>>>

\begin{rlemma}{Lemma}{\ref{lem:round-prob}}
Recall the noise is a mean-zero sub-Gaussian($\sigma^2$) random variable.
Let \LatePhase be a phase cutoff, 
and let $x_n, x'_n > 0$ be functions satisfying that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
\leq \frac{n x'_n}{2 \sigma}$,
for all $n \geq \LatePhase$.
Let $\tau_s$ be a stopping time
(which may depend on the entire past history)
which is almost surely in phase $s$,
i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
By the assumptions of the lemma,
the stopping time $\tau_s$ is such that almost surely,
each arm --- and in particular arm $i$ --- has been pulled at least
$s \geq \LatePhase$ times at time $\tau_s$.
Define $J$ to be the number of times that $i$ has been pulled at
time $\tau_s$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
renormalized to be a mean-zero sub-Gaussian($1/2$) random variable.
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
the stopping time $J$.
Specifically, we set $b = \frac{x_J^2}{16 \sigma^2}$,
and obtain that

@@

By Assmption~\ref{A1},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
is at most
$\TieDensity \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})
\leq \frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) \leq \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

### 2018-06-06 problem_setting.tex
changed gaussian noise to more general sub-gaussian noise

We consider a multi-armed bandit setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms are identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, and unknown to the agents
and the principal.
When arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps.
In fact, the analysis extends straightforwardly to any
continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
independent but not necessarily identically distributed across time.
\dkcomment{Are we actually stating the result in this generality now?
  If not, then why make the algorithm use continuity, as opposed to
  that we have Gaussians? If we do make the algorithm that general,
  then we should just define everything generally here.}}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
Here, $I_d$ denotes the $d \times d$ identity matrix.

>>>>

We consider a multi-armed bandit setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms are identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, and unknown to the agents
and the principal.
When arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent sub-Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps.
In fact, the analysis extends straightforwardly to any
continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
independent but not necessarily identically distributed across time.}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
Here, $I_d$ denotes the $d \times d$ identity matrix.
